Results

### 2018-09-27 4-results-simus.Rmd
new figures for pres

```{r}
myggplot <- function(..., coeff = 1) {
  ggplot(...) + 
    bigstatsr::theme_bigstatsr(size.rel = coeff) +
    theme(strip.text.x = element_text(size = rel(2)),
          strip.text.y = element_text(size = rel(2)))
} 
```

>>>>

```{r}
myggplot <- function(..., coeff = 1) {
  ggplot(...) + bigstatsr::theme_bigstatsr(size.rel = coeff)
} 
```

### 2018-09-27 results-simus-pres.Rmd
new figures for pres

---
title: "Results"
author: "Florian Privé"
date: "March 19, 2018"
output: 
  html_document:
    code_folding: hide
---

@@

```{r, message=FALSE}
library(tidyverse)

methods.color <- setNames(scales::hue_pal()(6), 
                          c("logit-simple", "PRS-max", "PRS-stringent",
                            "T-Trees", "logit-triple", "PRS-all")) 
```

```{r}
pAUC <- function(pred, target, p = 0.1) {
  val.min <- min(target)
  q <- quantile(pred[target == val.min], probs = 1 - p)
  ind <- (target != val.min) | (pred > q)
  tryCatch(bigstatsr::AUC(pred[ind], target[ind]) * p, 
           error = function(e) p^2 / 2)  # all same prediction
}

format_results <- function(results) {
  results %>%
    as_tibble() %>%
    filter(par.h2 == 0.8, par.dist == "gaussian") %>%
    mutate(
      par.causal = factor(map_chr(par.causal, ~paste(.x[1], .x[2], sep = " in ")),
                          levels = c("30 in HLA", paste(3 * 10^(1:3), "in all"))),
      AUC = map_dbl(eval, ~ bigstatsr::AUC(.x[, 1], .x[, 2])),
      pAUC = map_dbl(eval, ~ pAUC(.x[, 1], .x[, 2]))
    )
}
```

```{r}
boot <- function(x, n = 1e5, f = mean) {
  sd(replicate(n, f(sample(x, replace = TRUE))))
}
```

```{r}
myggplot <- function(..., coeff = 1) {
  bigstatsr:::MY_THEME(ggplot(...), coeff = coeff) +
  theme(strip.text.x = element_text(size = rel(2)),
        strip.text.y = element_text(size = rel(2)))
} 
```

```{r}
barplot_causal <- function(results, h2) {

  results %>%
    myggplot(aes(par.causal, AUC_mean, fill = method, color = method)) +
    geom_hline(yintercept = 0.5, linetype = 2) +
    geom_col(position = position_dodge(), alpha = 0.3) +
    geom_errorbar(aes(ymin = AUC_mean - 2 * AUC_boot, ymax = AUC_mean + 2 * AUC_boot),
                  position = position_dodge(width = 0.9), color = "black", width = 0.2) + 
    scale_y_continuous(limits = c(0.5, NA), minor_breaks = 0:20 / 20,
                       oob = scales::rescale_none) +
    labs(x = "Causal SNPs (number and location)", y = "Mean of 100 AUCs",
         fill = "Method", color = "Method") +
    scale_fill_manual(values = methods.color) +
    scale_color_manual(values = methods.color)
}

@@

```{r}
compare_logit <- function(results, with_method) {

  results <- filter(results, method %in% c("logit-simple", with_method))

@@

    results %>%
      myggplot() +
      geom_boxplot(aes_string("par.causal", y, color = "method", 
                              fill = "method"), alpha = 0.3) + 
      theme(axis.text.x = element_text(angle = 30, hjust = 1)) +
      labs(x = "Causal SNPs (number and location)", y = ylab, 
           fill = "Method", color = "Method") +
      theme(legend.position = "none") +
      scale_fill_manual(values = methods.color) +
      scale_color_manual(values = methods.color) +
      scale_y_continuous(limits = c(0, NA))
  }

@@

  p2 <- cowplot::plot_grid(
    plot_extra("nb.preds", "Number of predictors"),
    plot_extra("timing", "Execution time (in seconds)"),
    ncol = 1, align = "hv", scale = 0.90, 
    labels = LETTERS[2:3], label_size = 20
  )

@@

## Results with T-Trees

```{r}
results1 <- list.files("results1", full.names = TRUE) %>%
  map_dfr(~readRDS(.x)) %>%
  format_results()
```

```{r, out.width="90%", fig.width = 14}
compare_logit(results1, with_method = "T-Trees")

ggsave("figures/pres-ttrees.svg", scale = 1/100, width = 1300, height = 1060)
```

@@

```{r}
results2 <- list.files("results2", full.names = TRUE) %>%
  map_dfr(~readRDS(.x)) %>%
  format_results()

results2.summary <- results2 %>%
  group_by_at(c(vars(starts_with("par")), "method")) %>%
  summarise(AUC_mean = mean(AUC), AUC_boot = boot(AUC), N = n())
```

### Results with logit-triple

```{r, out.width="90%", fig.width = 14}
compare_logit(results2, with_method = "logit-triple")

ggsave("figures/pres-triple.svg", scale = 1/100, width = 1300, height = 1060)
```

@@

```{r}
results3 <- results2 %>%
  filter(par.model == "simple", method != "logit-triple")
```

@@

```{r}
results3.summary <- results3 %>%
  group_by_at(c(vars(starts_with("par")), "method")) %>%
  summarise(AUC_mean = mean(AUC), AUC_boot = boot(AUC), N = n())
```

```{r, fig.asp = 1, out.width = "60%", fig.width=8}
results3.summary %>%
  filter(method %in% c("logit-simple", "PRS-max")) %>%
  barplot_causal_one()

ggsave("figures/pres-AUC-logit.svg", scale = 1/110, width = 1045, height = 770)
```

```{r, fig.asp = 1, out.width = "60%", fig.width=8}
results3.summary %>%
  filter(grepl("PRS", method)) %>%
  barplot_causal_one()

ggsave("figures/pres-AUC-PRS.svg", scale = 1/110, width = 1045, height = 770)
```

@@

```{r}
results4 <- list.files("results4", full.names = TRUE) %>%
  map_dfr(~readRDS(.x)) %>%
  format_results()

results4 %>%
  group_by_at(c(vars(starts_with("par")), "method")) %>%
  summarise(AUC_mean = mean(AUC), AUC_boot = boot(AUC), N = n())

results34 <- rbind(
  cbind(simu = "all", results3),
  cbind(simu = "chr6", results4)
) %>%
  as_tibble()
```

```{r, fig.asp = 1, out.width = "90%"}
results34 %>%
  filter(par.h2 == 0.8, par.dist == "gaussian", method %in% c("logit-simple", "PRS-max")) %>%
  myggplot() +
  geom_hline(yintercept = 0.5, linetype = 2) +
  geom_hline(aes(yintercept = 0.94), linetype = 3, color = "blue") +
  geom_boxplot(aes(method, AUC, fill = simu, color = simu), alpha = 0.3) + 
  theme(axis.text.x = element_text(angle = 30, hjust = 1)) +
  facet_grid(. ~ par.causal) +
  scale_fill_brewer(type = "qual", palette = 2) +
  scale_color_brewer(type = "qual", palette = 2) + 
  labs(x = "Method")

ggsave("figures/pres-AUC-chr6.svg", scale = 1/110, width = 990, height = 700)
```

@@

```{r}
results5 <- list.files("results5", full.names = TRUE) %>%
  map_dfr(~readRDS(.x)) %>%
  format_results()

@@

results35.summary <- results3.summary %>%
  filter(par.causal == "300 in all") %>%
  cbind.data.frame(n.train = 6000) %>%
  bind_rows(results5.summary)
```

```{r}
results35.summary %>%
  filter(method %in% c("logit-simple", "PRS-max")) %>%
  myggplot(aes(n.train, AUC_mean, color = method, linetype = method)) +
  geom_hline(yintercept = 0.5, linetype = 2) +
  geom_hline(aes(yintercept = 0.94), linetype = 3, color = "blue") +
  geom_line(size = 1.5) +
  geom_errorbar(aes(ymin = AUC_mean - 2 * AUC_boot, 
                    ymax = AUC_mean + 2 * AUC_boot), 
                size = 1.5, width = 0) +
  scale_x_continuous(breaks = 1:6 * 1000, minor_breaks = NULL) + 
  scale_y_continuous(minor_breaks = 0:20 / 20) +
  scale_color_manual(values = methods.color) +
  labs(x = "Size of the training set", y = "Mean of 100 AUCs", 
       color = "Method", linetype = "Method") +
  theme(legend.key.width = unit(3, "line"))

ggsave("figures/pres-AUC-ntrain.svg", scale = 1/100, width = 870, height = 635)
```

>>>>

---
title: "Results"
author: "Florian Privé"
date: "September 27, 2018"
output: 
  html_document:
    code_folding: hide
---

@@

```{r, message=FALSE}
library(tidyverse)
library(pkg.paper.PRS)
options(nboot = 1e4)

COLORS <- scales::hue_pal()(6)
methods.color <- setNames(
  c(COLORS, COLORS[c(4, 2, 5)], "black"), 
  c("PLR", "C+T-max", "C+T-stringent", "T-Trees", "PLR3", "C+T-all",
    "C+T-max-0.05", "C+T-max-0.2", "C+T-max-0.8", "biglasso")
) 
```

```{r}
myggplot <- function(..., coeff = 1) {
  ggplot(...) + bigstatsr::theme_bigstatsr(size.rel = coeff)
} 
```

```{r}
barplot_causal <- function(results) {

  results %>%
    myggplot(aes(par.causal, AUC_mean, fill = method, color = method)) +
    geom_hline(yintercept = 0.5, linetype = 2) +
    geom_col(position = position_dodge(), alpha = 0.5, color = "black", size = 1) +
    geom_errorbar(aes(ymin = AUC_mean - 2 * AUC_boot, ymax = AUC_mean + 2 * AUC_boot),
                  position = position_dodge(width = 0.9), color = "black", width = 0.2, size = 1) + 
    scale_y_continuous(limits = c(0.5, NA), minor_breaks = 0:20 / 20,
                       oob = scales::rescale_none) +
    labs(x = "Causal SNPs (number and location)", y = "Mean of 100 AUCs",
         fill = "Method", color = "Method") +
    scale_fill_manual(values = methods.color) +
    scale_color_manual(values = methods.color)
}

@@

```{r}
compare_PLR <- function(results, with_method) {

  results <- filter(results, method %in% c("PLR", with_method))

@@

    results %>%
      myggplot() +
      geom_boxplot(aes_string("par.causal", y, color = "method", 
                              fill = "method"), alpha = 0.3) + 
      theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
      facet_grid(par.model ~ .) +
      labs(x = "Causal SNPs (number and location)", y = ylab, 
           fill = "Method", color = "Method") +
      theme(legend.position = "none") +
      scale_fill_manual(values = methods.color) +
      scale_color_manual(values = methods.color) +
      scale_y_continuous(limits = c(0, NA))
  }

@@

  p2 <- cowplot::plot_grid(
    plot_extra("nb.preds", "Number of predictors"),
    plot_extra("timing", "Execution time (in seconds)"),
    ncol = 1, align = "hv", scale = 0.95, 
    labels = LETTERS[2:3], label_size = 20
  )

@@

```{r}
corr <- readRDS("backingfiles/corr2.rds")
```

@@

```{r}
results2 <- list.files("results2", full.names = TRUE) %>%
  read_format_results(corr) %>%
  filter(par.h2 == 0.8, par.dist == "Gaussian")
```

### Results with PLR3

```{r, out.width="90%", fig.width = 14}
compare_PLR(results2, with_method = "PLR3")

ggsave("../thesis-docs/figures/pres2-triple.svg", scale = 1/100, width = 1300, height = 1060)
```

@@

@@

```{r}
results2.summary <- results2 %>%
  filter(par.model == "ADD", method != "PLR3") %>%
  group_by_at(c(vars(starts_with("par")), "method")) %>%
  summarise(AUC_mean = mean(AUC), AUC_boot = boot(AUC), N = n())
```

```{r}
results2.summary %>%
  filter(method %in% c("PLR", "C+T-max")) %>%
  barplot_causal_one()

ggsave("../thesis-docs/figures/pres2-AUC-logit.svg", scale = 1/110, width = 1045, height = 770)
```

```{r}
results2.summary %>%
  filter(grepl("C\\+T", method)) %>%
  barplot_causal_one()

ggsave("../thesis-docs/figures/pres2-AUC-PRS.svg", scale = 1/110, width = 1045, height = 770)
```

@@

```{r}
results4 <- list.files("results4", full.names = TRUE) %>%
  read_format_results(corr) %>%
  filter(par.h2 == 0.8, par.dist == "Gaussian")

results4.summary <- results4 %>%
  filter(method %in% c("PLR", "C+T-max")) %>%
  mutate(method = c_method_r2(method, thr.r2)) %>%
  group_by_at(c(vars(starts_with("par")), "method")) %>%
  summarise(AUC_mean = mean(AUC), AUC_boot = boot(AUC), N = n())

results2.all.r2 <- results2 %>%
  filter(par.model == "ADD", method %in% c("PLR", "C+T-max")) %>%
  mutate(method = c_method_r2(method, thr.r2)) %>%
  group_by_at(c(vars(starts_with("par")), "method")) %>%
  summarise(AUC_mean = mean(AUC), AUC_boot = boot(AUC), N = n())
```

```{r}
results4.summary %>%
  barplot_causal_one() + 
  geom_col(aes(par.causal, AUC_mean), data = results2.all.r2, 
           position = position_dodge(), color = "black", alpha = 0)

ggsave("../thesis-docs/figures/pres2-AUC-chr6.svg", scale = 1/110, width = 990, height = 700)
```

@@

```{r}
results5 <- list.files("results5", full.names = TRUE) %>%
  read_format_results(corr) %>%
  filter(par.h2 == 0.8, par.dist == "Gaussian")

@@

results35.summary <- results2.summary %>%
  cbind.data.frame(n.train = 6000) %>%
  bind_rows(results5.summary) %>%
  filter(par.causal == "300 in all")
```

```{r}
results35.summary %>%
  filter(method %in% c("PLR", "C+T-max")) %>%
  myggplot(aes(n.train, AUC_mean, color = method, linetype = method)) +
  geom_hline(yintercept = 0.5, linetype = 2) +
  geom_hline(aes(yintercept = 0.94), linetype = 3, color = "blue") +
  geom_line(size = 1.5) +
  geom_errorbar(aes(ymin = AUC_mean - 2 * AUC_boot, 
                    ymax = AUC_mean + 2 * AUC_boot), 
                size = 1.5, width = 0) +
  scale_x_continuous(breaks = 1:6 * 1000, minor_breaks = NULL) + 
  scale_y_continuous(minor_breaks = 0:20 / 20) +
  scale_color_manual(values = methods.color) +
  labs(x = "Size of the training set", y = "Mean of 100 AUCs", 
       color = "Method", linetype = "Method") +
  theme(legend.key.width = unit(3, "line"))

ggsave("../thesis-docs/figures/pres2-AUC-ntrain.svg", scale = 1/100, width = 870, height = 635)
```
